LaMachine: A meta-distribution for NLP software

### 2019-03-29 docs/lamachine_clarin2018.tex
[paper] reordered/rephrased some things

LaMachine exists since since May 2015 and has been installed extensively ever since by numerous users. In early 2018 version 2 was
released which was a significant redesign, powered by Ansible\footnote{\url{https://www.ansible.com}}. We ourselves use
LaMachine as a means by to make our full software stack available to end-users, whether those be individual researchers, research
groups, or hosting providers like CLARIN centres. LaMachine has in fact been adopted in all of those areas. Quantifying its
actual use is not trivial despite having some tracking solutions in place, but can roughly be put at around one or two
installations or upgrades \emph{every day}. We also see a regular influx of questions on our issue tracker, indicating
community interest.

@@

>>>>

LaMachine exists since May 2015 and has been installed extensively ever since by numerous users. Quantifying its actual
use is not trivial despite having sme tracking solutions in place, but our statistics show that LaMachine was installed at least over a thousand times, on
machines in over 25 different countries since its inception\footnote{https://applejack.science.ru.nl/lamastats/lamachinestats.html}. In early 2018 version 2 was released which was a significant redesign, powered
by Ansible\footnote{\url{https://www.ansible.com}}. We ourselves use LaMachine as a means by to make our full software
stack available to end-users, whether those be individual researchers, research groups, or hosting providers like CLARIN
centres. LaMachine has in fact been adopted in all of those areas. We also see a regular influx of questions on our issue tracker, indicating community interest.

@@

LaMachine is most often used by a researcher or data scientist who installs LaMachine on his own computer (locally, in a
local environment or as a Docker container or VM). Here we discuss two case studies where LaMachine was used under
circumstances that go beyond this most common usage of LaMachine: using LaMachine on a secure server without internet
connection, and using LaMachine to provide a work environment for a group of researchers.
